lab_notebook

### 2019-01-12 documents/figs-and-calcs.Rmd
figure 2: mapping countries with an without ITQs

>>>>

library(sf)
library(ggplot2)
#library(tmap)

projection_data_fig2 <- readRDS(here("data","projection_data.rds")) %>% 
  filter(Scenario == "Historic") %>%
  #group_by(IdOrig) %>% 
  filter(Year == max(Year))%>%
  filter(Dbase != "SOFIA") %>%
  filter(IdLevel != "Neis") %>%
  select(Country, CatchShare) %>%
  distinct() %>%
  filter(CatchShare == "1")

colnames(projection_data_fig2) <- c("CNTRY_NAME","CatchShare")
projection_data_fig2[projection_data_fig2 =="USA"] <- "United States"
projection_data_fig2$CatchShare <- as.factor(projection_data_fig2$CatchShare)

#alreay in 4326; projection = WGS84
countries <- st_read(dsn = "countries_shapefiles", layer = "Countries_WGS84")%>%
  select(CNTRY_NAME)
#plot(countries)

projection_spatial <- merge(projection_data_fig2, countries, by = "CNTRY_NAME", all.y =TRUE)
projection_spatial$CatchShare <- as.numeric(projection_spatial$CatchShare)
projection_spatial[is.na(projection_spatial)] <- 0
projection_spatial$CatchShare <- as.factor(projection_spatial$CatchShare)
projection_spatial <- st_as_sf(projection_spatial)

fig_2 = ggplot() +
  geom_sf(data= projection_spatial, aes(fill = CatchShare))

fig_2

### 2019-01-12 lab_notebook.Rmd
figure 2: mapping countries with an without ITQs

#cooperative data from "Conservation incentives and collective choices in cooperative fisheries" paper (Ovando et al 2013)
jc_coop <- read_csv("data/clean_cooperatives_data.csv")

@@

>>>>

#cooperative data from "Conservation incentives and elective choices in cooperative fisheries" paper (Ovando et al 2013)
jc_coop <- read_csv("data/clean_cooperatives_data.csv")

@@

1/11/2019

geom_point(stat=, fun.y="medium") +
    stat_summary(fun.y="medium", geom="point")
